### 2018-07-11 manuscript.tex
Update manuscript.tex

\subsubsection{Measurements and Concepts}\label{measurements-and-concepts}
---- benefirs of fgc is value (what fulfilment/benefits/positivity someone get by performing certain behaviors), not attitude,

@@

--- community levels of impact and intervention
\cite{Drot11, Grue05, JoneEhir04} (both on cultural perspective, and maybe norm), 
\cite{ChegAske04}(community -based approach), \cite{BrowBeec13,PatrSing15}

>>>>

\subsubsection{Measurements and Concepts}\label{measurements-and-concepts}

@@

--- community levels of impact and intervention
\cite{Drot11, Grue05, JoneEhir04} (both on cultural perspective, and maybe norm), 
\cite{ChegAske04}(community -based approach), \cite{BrowBeec13,PatrSing15}
\cite{TerrHogg96}:  subjective norm on attitude and planned behavior
\cite{EffeVogt15}:  Efferson proposed that cutting is not a social norm based on "coordination."  The problem is that he and his colleages conclusion was based on a marraige market associating with cutting.  But it is likely that fgc is much less an action for marraige proposal but a social indentity to the group they indentify with.
